
%mainfile: Multimodal_learning.tex

\vspace{-0.3em}
\bibliographystyle{abbrv}
\begin{thebibliography}{99}

{\footnotesize

\bibitem{M. Asadi-Aghbolaghi 2017}
  M. Asadi-Aghbolaghi, A. Clapés, M. Bellantonio, H. J. Escalante, 
  V. Ponce-López, X. Baró, I. Guyon, S. Kasaei, and S. Escalera. 
  A Survey on Deep Learning Based Approaches for Action and Gesture 
  Recognition in Image Sequences. 
  In \textit{Automatic Face \& Gesture Recognition (FG 2017) 2017 12th IEEE
  International Conference}, 2017.

\bibitem{T. Baltrusaitis 2017}
  T. Baltrusaitis, C. Ahuja and L-P. Morency. Multimodal Machine Learning:
  A Survey and Taxonomy. In \textit{arXiv preprint arXiv: 1705.09406}, 2017.

\bibitem{Y. Bengio 2012}
  Y. Bengio. Practical recommondations for gradient-based training of deep
  architectures. In \textit{Neural networks: Tricks of the trade},
  pages 437--478, 2012.

\bibitem{Y. Bengio 2013}
  Y. Bengio, L. Yao, G. Alain and P. Vincent. Generalized denoising
  auto-encoders as generative models. In \textit{Advances in Neural
  Information Processing Systems}, pages 899--907, 2013.

\bibitem{C. Bregler 1994}
  C. Bregler and Y. Konig. ``Eigenlips'' for robust speech recognition.
  In \textit{ICASSP}, 1994.

\bibitem{A. Clark 1997}
  A. Clark. Being there: Putting brain, body, and world together again.
  In \textit{MIT press}, 1997.

\bibitem{L. Deng 2013}
  L. Deng, G. Hinto and B. Kinsbury. New types of deep neural network
  learning for speech recognition and related applications: An overview.
  In \textit{ICASSP}, 2013.

\bibitem{A. Droniou 2014}
  A. Droniou, S. Ivaldi, and O. Sigaud. A deep unsupervised network
  for multimodal perception, representation and classification. In
  \textit{Robotics and Autonomous System}, 2014.

\bibitem{A. Frome 2013}
  A. Frome, G. S. Corrado, J. Shlens, S. Bengio, J. Dean,
  T. Mikolov, et al. Devise: A deep visual-semantic embedding model. 
  In \textit{NIPS}, 2013.

\bibitem{A. Graves 2013}
  A. Graves. Generating sequences with recurrent neural networks.
  In \textit{arXiv preprint arXiv:1308.0850}, 2013.

\bibitem{S. Harnad 1990}
  S. Harnad. The symbol grounding problem. In \textit{Physica D}, vol. 42,
  pages 335–346, 1990.

\bibitem{G. Hinton 2012}
  G. Hinton, L. Deng, D. Yu, G. Dahl, A. Mohamed, N. Jaitly, A. Senior, V.
  Vanhoucke, P. Nguyen, T. Sainath and B. Kingsbury. Deep neural networks
  for acoustic modeling in speech recognition.
  In \textit{IEEE Signal Processing Mag} Vol. 29, 2012.

\bibitem{S. Ioffe 2015}
  S. Ioffe and C. Szegedy. Batch normalization, accelerating deep network
  training by reducing internal covaraiate shift. In \textit{International
  Conference on Machine Learning}, pages 448--456, 2015.

\bibitem{S. Ji 2013}
  S. Ji, W. Xu, M Tang and K. Yu. 3D Convolutional Neural Networks
  for Human Action Recognition. In \textit{IEEE Transactions on Pattern
  Analysis and Machine Intelligence}, vol. 35, 2013.

\bibitem{A. Karpathy 2015}
  A. Karpathy, and L. Fei-Fei. Deep visual-semantic alignments for
  generating image descriptions. In \textit{Proceedings of the IEEE
  Conference on Computer Vision and Pattern Recognition},
  pages 3128--3137, 2015.

\bibitem{A. K. Katsaggelos 2015}
  A. K. Katsaggelos, S. Bahaadini and R. Molina. Audiovisual fusion:
  Challenges and new approaches. In \textit{Proceedings of the IEEE},
  vol. 103, 2015.

\bibitem{D. Kingma 2014}
  D. Kingma and J. Ba. Adam: A method for stochastic optimization.
  In \textit{arXiv preprint arXiv:1412.6980}, 2014.

\bibitem{A. Krizhevsky 2012}
  A. Krizhevsky, I. Sutskever, and G. E. Hinton.  ImageNet Classification
  with Deep Convolutional Neural Networks. In \textit{NIPS}, 2012.

\bibitem{Y. LeCun 1998}
  Y. LeCun, L. Bottou, Y. Bengio and P. Haffner. Gradient-based
  learning applied to document recognition. In \textit{Proceedings of the
  IEEE}, vol. 86, pages 2278--2324, 1998.

\bibitem{Y. LeCun 2010}
  Y. LeCun, K. Kavukcuoglu and C. Farabet. Convolutional networks and
  apllications in vision. In \textit{Circuits and Systmes (ISCAS), 
  Proceedings of 2010 IEEE International Symposium}, pages 253--256, 2010.

\bibitem{A. Makhzani 2014}
  A. Makhzani and B. Frey, K-Sparse autoencoders. In \textit{International
  Conference on Learning Representations (ICLR)}, 2014.

\bibitem{J. Masci 2011}
  J. Masci, U. Meier, D. C. ̧san, and J. Schmidhuber.
  Stacked convolutional auto-encoders for hierarchical feature extraction.
  In \textit{Artificial Neural Networks and Machine Learning–ICANN}, 2011.

\bibitem{I. Matthews 2002}
  I. Matthews, T. F. Cootes, J. A. Bangham and S. Cox. Extraction of visual
  features for lipreading. In \textit{PAMI}, 2002.

\bibitem{A. Memo 2015}
  A. Memo, L. Minto and P. Zanuttigh.  Exploiting Silhouette Descriptors and
  Synthetic Data for Hand Gesture Recognition. In \textit{STAG: Smart
  Tools \& Apps for Graphics}, 2015.

\bibitem{A. Memo 2017}
  A. Memo and P. Zanuttigh. Head-mounted gesture controlled interface
  for human-computer interaction. In \textit{Multimedia Tools and
  Applications}, 2017.

\bibitem{S. Mitra 2007}
  S. Mitra and T. Acharya. Gesture recognition: A survey. 
  In \textit{IEEE Systems, Man, and Cybernetics}, 37:311–324, 2007. 

\bibitem{P. Molchanov 2015}
  P. Molchanov, S. Gupta, K. Kim, and J. Kautz. Hand gesture recognition 
  with 3D convolutional neural networks. In \textit{CVPRW}, 2015.

\bibitem{S. Molholm 2002}
  S. Molholm, W. Ritter, M. M. Murray, D. C. Javitt, C. E. Schroeder,
  and J. J. Foxe. Multisensory auditory–visual interactions during early
  sensory processing in humans: a high-density electrical mapping study.
  In \textit{Cognitive brain research}, 14:115--128, 2002.

\bibitem{S. Moon 2015}
  S. Moon, S. Kim and H. Wang. Multimodal transfer deep learning with
    applications in audio-visual recognition. In \textit{NIPS MMML
    Workshop}, 2015.

\bibitem{J. Nagi 2011}
  J. Nagi, F. Ducatelle, G. Di Caro, D. Ciresan, U. Meier, A. Giusti,
  F. Nagi, J. Schmidhuber, and L. Gambardella.
  Max-pooling convolutional neural networks for vision-based hand 
  gesture recognition.
  In \textit{Proceedings of the IEEE International Conference on
  Signal and Image Processing Applications}, 2011.

\bibitem{N. Neverova 2013}
  N. Neverova, C. Wolf, G. Paci, G. Sommavilla, G. W. Taylor,and F. Nebout.
  A multi-scale approach to gesture detection and recognition.
  In \textit{Computer Vision Workshops (ICCVW)}, 2013.

\bibitem{N. Neverova 2014}
  N. Neverova, C. Wolf, G. W. Taylor, and F. Nebout.  Multiscale deep
  learning for gesture detection and localization. In \textit{ECCVW}, 2014.

\bibitem{J. Ngiam 2011}
  J. Ngiam, A. Khosla, M. Kim, J. Nam, and A. Y. Ng. 
  Multimodal deep learning. In:
  In \textit{International Conference on Machine Learning}.  28. 
  Bellevue, Washington, USA, 2011.

\bibitem{K. Noda 2014}
  K. Noda, Y. Yamaguchi, K. Nakadai, H. G. Okuno and T. Ogata. Audio-visual
  speech recognition using deep learning.  In \textit{Applied Intelligence},
  vol. 42, no. 4, pp. 722–737, 2014.

\bibitem{H. Noh 2015}
  H. Noh, S. Hong and  B. Han.  Learning deconvolution network for semantic
  segmentation. In 2015 IEEE International Conference on Computer Vision
  (ICCV), pages 1520--1528, 2015.

\bibitem{J. Piaget 1952}
  J. Piaget. \textit{The origins of intelligence in children.}
  WW Norton \& Co, 1952.

\bibitem{L. Pigou 2014}
  L. Pigou, S. Dieleman, P. J. Kindermans, and B. Schrauwen.
  Sign language recognition using convolutional neural networks. In
  \textit{Workshop at the European Conference on Computer Vision},
  pages 572--578, 2014.

\bibitem{G. Potamianos 2004}
  G. Potamianos, C. Neti, J. Luettin and  I. Matthews. Audio-visual
  automatic speech recognition: An overview. In \textit{Issues in Visual
  and Audio-Visual Speech Processing, MIT Press}, 2004.

\bibitem{N. Pugeault 2011}
  N. Pugeault, and R. Bowden. Spelling It Out: Real-Time ASL
  Fingerspelling Recognition. In \textit{Proceedings of the 1st IEEE
  Workshop on Consumer Depth Cameras for Computer Vision}, 2011.

\bibitem{A. Radford 2015}
  A. Radford, L. Metz, and S. Chintala. Unsupervised representation
  learning with deep convolutional generative adversarial networks. In 
  \textit{arXiv preprint arXiv:1511.06434}, 2015.

\bibitem{L. Smith 2005}
  L. Smith and M. Gasser. The development of embodied cognition:
  Six lessons from babies. In \textit{Artificial life}, 11:13--29, 2005.

\bibitem{R. Socher 2013}
  R. Socher, M. Ganjoo, H. Sridhar, O.Bastani, C. D. Manning, and
  A. Y. Ng. Zero-shot learning through cross-modal transfer.
  In \textit{International Conference on Learning Representations (ICLR)},
  Scottsdale, Arizona, USA, 2013.

\bibitem{N. Srivastava 2014}
  N. Srivastava, G. Hinton, A. Krizhevsky, I. Sutskever and R. Salakhutdinov.
  Dropout: A simple way to prevent neural networks from overfitting. In
  \textit{Journal of Machine Learning Research}, vol. 15, 2014.

\bibitem{T. Starner 1998}
  T. Starner, A. Pentland, and J. Weaver. Real-time american sign language
  recognition using desk and wearable computer based video. 
  In \textit{PAMI}, 20(12):1371–1375, 1998.

\bibitem{J. Sung 2017}
  J. Sung, I. Lenz, and A. Saxena. Deep multimodal embedding:
  Manipulating novel objects with point-clouds, language and trajectories.
  In \textit{Robotics and Automation (ICAR), 2017 IEEE International
  Conference}, pages 2794--2801, 2017.

\bibitem{I. Sutskever 2014}
  I. Sutskever, O. Vinyals, and Q. V. Le. Sequence to sequence learning
  with neural networks. In \textit{Advances in neural information
  processing systems}, pages 3104--3112, 2014.

\bibitem{C. Szegedy 2017}
  C. Szegedy, S. Ioffe, V, Vanhoucke. Inception-v4, inception-ResNet and the
  impact of residual connections on learning. In \textit{AAAI},
  pages 4278--4284, 2017.

\bibitem{V. Turchenko 2017}
  V. Turchenko, E. Chalmers and A. Luczak. A deep convolutional auto-encoder
  with pooling -- unpooling layers in Caffe. In \textit{arXiv preprint
  arXiv:1701.04949}, 2017.

\bibitem{P. Vincent 2008}
  P. Vincent, H. Larochelle, Bengio and P.-A. Manzagol.
  Extracting and composing robust features with denoising autoencoders.
  In \textit{Proceedings of the 25th international conference
  on Machine Learning (ICML)}, pages 1096--1103; 2008.

\bibitem{P. Vincent 2010}
  P. Vincent, H. Larochelle, I. Lajoie, Y. Bengio and P.-A. Manzagol.
  Stacked denoising autoencodes: Learning useful representations in a
  deep network with a local denoising criterion? In \textit{The Journal
  of Machine Learning Research}, vol. 11, pages 3371--3408, 2010.

\bibitem{J. Weng 2001}
  J. Weng, J. McClelland, A. Pentland, O. Sporns, I. Stockman, M. Sur,
  and E. Thelen. Autonomous mental development by robots and animals.
  In \textit{Science}, vol. 291, no. 5504, pages 599–600, 2001.

\bibitem{J. Weston 2010}
  J. Weston, S. Bengio, and N. Usunier. 
  Large scale image annotation: learning to rank with joint word-image
  embeddings. In \textit{Machine Learning}, 81(1):21--35, 2010.

\bibitem{D. Wu 2016}
  D. Wu, L. Pigou, P.-J. Kindermans, N. D.-H. Le, L. Shao,
  J. Dambre, and J.-M. Odobez. 
  Deep Dynamic Neural Networks for Multimodal Gesture Segmentation and
  Recognition. In \textit{Pattern Analysis and Machine Intelligence
  IEEE Transactions}, vol. 38, 2016.

\bibitem{B. P. Yuhas 1989}
  B. P. Yuhas, M. H. Goldstein, and T. J. Sejnowski. Integration of acoustic
  and visual speech signals using neuralnetworks. In \textit{IEEE Comm.
  Magazine}, pp. 65--71, 1989.

\bibitem{M. D. Zeiler 2011}
  M. D. Zeiler, G. W. Taylor and R. Fergus.
  Adaptive deconvolutional networks for mid and high level feature learning.
  In \textit{Computer Vision (ICCV), 2011 IEEE International Conference},
  pages 2018--2025, 2011.

}

\end{thebibliography}
